---
title: "General plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{General plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r message=FALSE, warning=FALSE}
library(Biorplot)
```



## Bior_LinePlot()

Line plot use line segments to connect data points to show data trends. Each data point represents a specific time point or value, and the line segments reflect the relationship between data points. Line plot are usually used to display time series data, trend analysis, cyclical changes, etc.

In `Biorplot` package, we use the `Bior_LinePlot()` function to draw a line plot.

### Base linePlot

Draw a base line plot with different type:

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
data <- data.frame('x' = c(1:20), 'y' = rnorm(20), 'Type' = rep(c('A','B'), 10))
palette <- c("#f89588","#63b2ee")
Bior_LinePlot(data, x = "x", y = "y", color = "Type", title = "Test Bior_LinePlot",
              palette = palette, plot_type = "l", size = 2, text.size = 30,
              ggtheme = theme_minimal()) +
  font("title", size = 35)
```


### Correlation linePlot

Draw a line plot with correlation coefficient R and P-value:

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
data <- data.frame('x' = c(1:10), 'y' = c(1,1.5,1.8,2.3,3.3,5.3,7.5,8,9,10))

Bior_LinePlot(data, x = "x", y = "y",
              color = "firebrick3", plot_type = "l", size = 2, 
              cor.test = TRUE, cor.label.x=1, cor.label.y=9, R.digits = 2, P.digits = 2,
              cor.label.size = 10,
              text.size = 30, ggtheme = theme_classic()) +
  geom_point(color="black", fill="firebrick3", shape=21, size=4, stroke=1) +
  font("title", size = 30)
```





## Bior_PiePlot()

Pie plot are often used to show the relative proportions of data. Based on a circular pattern, it divides the data into different sectors, and the size of each sector represents the relative size of the corresponding data. Pie plot can intuitively show the proportional relationship between different data, helping observers quickly understand the data distribution.

In `Biorplot` package, we use the `Bior_PiePlot()` function to draw a Pie plot.

### Base PiePlot

Draw a base pie plot with different type:

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
value <- c(0.1,0.2,0.4,0.1,0.3)
type <- c("A (10%)", "B (20%)", "C (40%)", "D (10%)", "E (30%)")
col <- c("#AEC7E8B2", "#FFBB78B2", "#98DF8AB2", "#FF9896B2", "#C5B0D5B2")
p <- Bior_PiePlot(value=value, type=type, col=col, title="Test Bior_pie")
p
```

### PiePlot with label

Draw a pie plot with text labels

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
value <- c(0.1,0.2,0.4,0.1,0.3)
type <- c("A", "B", "C", "D", "E")
label <- c("10%","20%","40%","10%","30%")
col <- c("#1F77B4B2", "#FF7F0EB2", "#2CA02CB2", "#D62728B2", "#9467BDB2")
p <- Bior_PiePlot(value=value, type=type, label=label, col=col, title="Test Bior_pie", label.x=1.2, label.color="white", label.size=5)
p
```





## Bior_BarPlot()

Bar plot is usually used to compare two or more values (at different times or under different conditions) using the length of the rectangle as a variable. It is usually used for analyzing smaller data sets.

In `Biorplot` package, we use the `Bior_BarPlot()` function to draw a Bar plot.

### Base BarPlot

Draw a basic bar chart:

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
df <- data.frame(
  x = c("A", "B", "C"),
  y = c(3, 2, 1))
Bior_BarPlot(df, "x", "y", fill = "steelblue", color = "steelblue")
```

### stack BarPlot

Draw a stacked bar plot and add text label:

```{r fig.height=4, fig.width=6, message=FALSE, warning=FALSE}
df <- data.frame(
  x = rep(c('sample1','sample2','sample3','sample4'), each=2),
  y = c(20,16,29,16,14,11,22,21),
  type = rep(c('gene1','gene2'), 4),
  label = c(20,16,29,16,14,11,"","")
)
col <- c("#AEC7E8FF","#FFBB78FF")
Bior_BarPlot(df, "x", "y", fill = "type", color = "type", label = df$label,
                  palette = col, lab.pos = "in") +
  theme(legend.position = "right", legend.key.size=unit(1, "cm"))
```

### dodged BarPlot

Change position: Interleaved (dodged) bar plot: 

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
Bior_BarPlot(df, "x", "y", fill = "type", color = "type", palette = col,
                  label = TRUE, position = position_dodge(0.9))
```




## Bior_DotPlot()

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
x <- rep(paste('sample', 1:5, sep=''), 4)
y <- rep(paste('gene', 1:4, sep=''), 5)
size <- round(rnorm(20, mean = 10, sd = 5))
colour <- c("#1F77B4FF","#FF7F0EFF","#2CA02CFF","#D62728FF","#9467BDFF")
p <- Bior_DotPlot(x = x, y = y, size = size, group.by = x, colour = colour, max_size=10)
p
```



## Bior_Sankeyplot()

```{r fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
# links data, colnames must have 'source' 'target' 'value'
links <- data.frame(
  source=c("C","A", "B", "E", "D"), 
  target=c("b","c", "a", "e", "d"), 
  value=c(1, 2, 0, 4, 5)
)

# Set Nodes order and colour
Nodes.order <- c("A", "B", "C", "D", "E", "a", "b", "c", "d", "e")
Nodes.colour <- c("#1F77B4B2","#FF7F0EB2","#2CA02CB2","#D62728B2","#9467BDB2",
                  "#8C564BB2","#E377C2B2","#7F7F7FB2","#BCBD22B2","#17BECFB2")
p <- Bior_Sankeyplot(links, Nodes.order=Nodes.order, Nodes.colour=Nodes.colour, fontSize=20)
p
# Use saveNetwork() to save the plot as html
# saveNetwork(p,"sankey.html")
```





